---
title: "13.1 Basics"
output: html_notebook
---

1. The most important S3 objects in base R are factors, data frames, and date/times (Dates, POSIXct, POSIXlt). You’ve already seen the attributes and base type that factors are built on. What base types and attributes are the others built on?
```{r factor}
f <- factor("a")
typeof(f)
attributes(f)
```
```{r data frame}
df <- data.frame(x = 1:10)
typeof(df)
attributes(df)
```
```{r Dates}
d <- as.Date("2017-09-22")
typeof(d)
attributes(d)

ct <- as.POSIXct("2017-09-22")
typeof(ct)
attributes(ct)

lt <- as.POSIXlt("2017-09-22")
typeof(lt)
attributes(lt)


```




2. Describe the difference in behaviour in these two calls.
```{r q2}
set.seed(1014)
some_days <- as.Date("2017-01-31") + sample(10, 5)

mean(some_days)
#> [1] "2017-02-05"

mean(unclass(some_days))

#> [1] 17202
```
mean(some_days) is passed an object of class "date" so the mean.Date method is
called
mean(unclass(some_days)) is passed a numeric vector so the default mean method is called

What does the following code return? What base type is it built on? What attributes does it use?

```{r ecdf}
x <- ecdf(rpois(100, 10))
x
#> Empirical CDF 
#> Call: ecdf(rpois(100, 10))
#>  x[1:18] =  2,  3,  4,  ..., 2e+01, 2e+01

typeof(x)
attributes(x)

```
returns a function (or closure).  Base type is closure



